---
title: "Data Structure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Data Structure}
  %\usepackage[UTF-8]{RtD3}
---

## Overview  

RtD3 has strict requirements for the format of input data. Below, The structure of each input dataset is described in detail.  


## geoData  
Geodata should be an `sf` object that must contain the columns:  
  
`"sovereignt", "geometry"`  
  
## summaryData  
  
summaryData should be a `data.frame` that must contain the columns:  
  
`"Country", "New confirmed cases by infection date", "Expected change in daily cases", "Effective reproduction no.", "Rate of growth", "Doubling/halving time (days)"`  
  
## rtData
  
rtData should be a JSON-like list object, containing either `data.frame` values or `NULL` values.  
  
rtData can have an arbitrary number of entries, allowing for the visualization of rts from multiple data sources.   
  
All `data.frame` values in rtData must contain the columns:  
  
`"country","date","type","median","lower_90","upper_90","lower_50","upper_50"`  

All entries in the rtData list must contain the values:  
   
`"rtData", "casesInfectionData", "casesReportData", "obsCasesData"`  
  
`"rtData"` - R estimates  
`"casesInfectionData"` - Cases by date of infection estimates  
`"casesReportData"` - Cases by date of report estimates  
`"obsCasesData"` - Observed case data  

An example of the overall structure of an rtData list from two data sources ("Cases" and "Deaths"):

``` {r eval = F}

rtData = list('Cases' = list('rtData' = rtData, 
                             'casesInfectionData' = casesInfectionData, 
                             'casesReportData' = casesReportData, 
                             'obsCasesData' = obsCasesData),
              'Deaths' = list('rtData' = rtData_death, 
                             'casesInfectionData' = casesInfectionData_death, 
                             'casesReportData' = casesReportData_death, 
                             'obsCasesData' = obsCasesData_death))

```

An example of the overall structure of an rtData list with some `NULL` values:

``` {r eval = F}

rtData = list('Cases' = list('rtData' = rtData, 
                             'casesInfectionData' = NULL, 
                             'casesReportData' = casesReportData, 
                             'obsCasesData' = NULL))

```


