---
title: "Detailed Configuration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Detailed Configuration}
  %\usepackage[UTF-8]{RtD3}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(RtD3)
```

## Overview

RtD3 has a number of features that are not required, but can improve the output of a visualization. 

These features include:

* Toggling multiple data sources
* Linking to more detailed estimates
* Plotting flexible geographies

## Detailed visualization

We will prepare the geoData by resolving the USA name conflict between the geoData and estimates.

``` {r}
geoData <- rnaturalearth::ne_countries(returnclass = 'sf')


geoData <- geoData %>% 
  mutate(sovereignt = ifelse(sovereignt == 'United States of America', 'United States', sovereignt))
```

We will also add a second data source to the rtData. Here, rtData will have two items, "Cases" and "Deaths". These labels are flexible and are passed to the dataset selector dropdown. Data can be extracted from `EpiNow2` easily using the `RtD3::readInEpinow2` function or as a list from other sources. 


``` {r}
# Define the base URL/file path for the estimates
base_url <- 'https://raw.githubusercontent.com/epiforecasts/covid-rt-estimates/master/national/'

# Read in each summary folder
rtData <- list("Cases" = RtD3::readInEpiNow2(path = paste0(base_url, "cases/summary")),
               "Deaths" = RtD3::readInEpiNow2(path = paste0(base_url, "deaths/summary")))

# Extract summary data from cases
summaryData <- rtData$Cases$summary

## Drop remaining summary data
rtData <- lapply(rtData, function(.){.[-1]})
```

We can also configure a list of URLs to link more detailed estimates (using the `RtD3::getSubregionalUrls` helper function).

``` {r}
subnational_ref <- RtD3::getSubregionalUrls(path = "https://epiforecasts.io/covid/posts/national/",
                                            areas = c('Afghanistan', 'Brazil', 'Colombia', 'India', 
                                                      'Italy', 'Germany', 'Russia', 'United Kingdom',
                                                      'United States'))
```

The data and config are then passed to `RtD3::summaryWidget`.

``` {r}
RtD3::summaryWidget(
  geoData = geoData,
  summaryData = summaryData,
  rtData = rtData,
  subregional_ref = subnational_ref
)
```
