---
title: "Creating an RtD3 visualization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Creating an RtD3 visualization}
  %\usepackage[UTF-8]{RtD3}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rnaturalearth)
library(RtD3)
```

## Overview

RtD3 creates interactive visualizations of rt estimates using JavaScript, React, and D3. Plots can be added to the RStudio Viewer, included in R Markdown documents, or embedded in a Shiny app.

This package is closely linked to the estimates produced by the [EpiNow2](https://epiforecasts.io/EpiNow2/) package, an open source resource for creating rt estimates.

## Basic visualization

RtD3 is flexible and will attempt to generate an interactive visualization with whatever data set it receives. Columns must be in a standard format (detailed in the "Data Structure" documentation). 

This example relies on estimates from [epiforecasts covid-rt-estimates](https://github.com/epiforecasts/covid-rt-estimates).

```{r }
base_url <- 'https://raw.githubusercontent.com/epiforecasts/covid-rt-estimates/master/national/'

geoData <- rnaturalearth::ne_countries(returnclass = 'sf')

rtData <- list("Cases" = RtD3::readInEpiNow2(
  path = "https://raw.githubusercontent.com/epiforecasts/covid-rt-estimates/master/national/cases/summary",
  region_var = "country"
  ))
```

Rt data is passed to the visualization function in a JSON-like list of lists to allow for visualization of estimates from different data sources. Rt data should be prepared in the format `{'Source':{'rtData':x, 'casesInfectionData':x, 'casesReportData':x, 'obsCasesData':x, 'summaryData':x}, ...}`. All required datasets are then passed to the visualization function.


``` {r}
RtD3::summaryWidget(
  geoData = geoData,
  rtData = rtData,
)
```

